A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-08-02 paper/elsarticle/elsarticle-template.tex
paper

\begin{abstract}
Augmented reality (AR) promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene, potentially reducing or altogether obviating the need for workers to refer to instructions in paper form or on a screen. \textit{Spatial} AR, in turn, is a form of AR whereby the augmentation of the scene is carried out using a projector, with the advantage of rendering the augmentation visible to all onlookers simultaneously without calling for each to wear some form of head-mounted display. In carrying out spatial AR, however, care must be taken to appropriately warp the images to be projected in a manner that they appear free of distortions to the viewer. For planar scene geometry (such as a floor, wall, or table), this can be done in a cumbersome manual process called keystone correction, often using software bundled with the projector. %, since the geometry of the scene as it relates to the geometry of the projector plays a role in how the pixels of the projector's image plane map to points in the scene

@@

Correcting for projective distortions of the sort outlined in Section~\ref{sec:intro} can be achieved by modeling the manner in which the respective rays through the pixels of the projector's image plane fan out into the scene (i.e., by `calibrating' the projector) and the geometry of the scene itself (i.e., by recovering the scene plane relative to the projector) within at least the projector's field of view. This is because the scene point `illuminated' by a pixel in the projector's image plane can be recovered by intersecting its corresponding ray with the geometry of the scene surface. To model this interaction, we (i) carry out a one-time projector calibration, which in our approach calls for additionally calibrating a camera facing downward to the scene plane and includes recovery of the scene plane as a convenient side effect. Next, we use the relative camera-projector-scene plane geometry to (ii) compute a plane-induced homography that warps the image to be projected in a manner that it appear undistorted to the viewer, and placed in alignment with the axes of a proxy image of the scene. These two points are treated in Sections~\ref{sec:approach:geometry} and \ref{sec:approach:homography}, respectively.

@@

\begin{figure}
    \centerline{\includegraphics[scale=.35]{images/2d3d.png}}
    \caption{Scene plane (gray) recovered via spatial resection with respect to 2D-3D correspondences obtained using a chessboard pattern (blue); 3D circle center points of the asymmetrical circle pattern---i.e., the 3D positions of the 2D-3D correspondences to be used for calibrating the projector---obtained by intersection with the scene plane of back-projections (likewise gray) of the 2D circle center points of the asymmetrical circle pattern detected in the image plane (red). Note that as in the figures that follow, the rendering in the figure corresponds to the projection calibration image in Figure~\ref{fig:2d}(b), acquired by the downwards-facing camera (frustum of the camera in black, with up vector in red).}
    \label{fig:3d}
\end{figure}

@@

Owing to the manner in which we place the virtual projector, the virtual projector's axes and thus the augmentation are aligned with the axes of the downward-facing camera; the placement of the camera thereby intuitively determines the principal axes according to which augmentations are to be placed. Note further that a consequence of placing the virtual projector by rotating about the point of intersection of the projector's optical axis with the scene plane is that \textit{the center of the projector's image plane remains invariant} to the placement of the virtual projector, i.e., a steerable mirror can be aimed with respect to a point projected from the center of the projector's image plane, further facilitating placement of augmentations.

@@

The hardware setup employed in the evaluation (cf.\ Figure \ref{fig:eval}(a)) comprised a Panasonic PT-RZ660BE projector with a steerable mirror system---used in our experiments to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute \cite{rupprecht2020information,Rupprecht2021}. The steerable mirror system was bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a downward-facing Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The floorspace used for our experiments measured dimensions of ca.\ 6~m~$\times$~4~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m.

@@

\paragraph{Our approach} We began by carrying out a calibration of the camera, acquiring 10 camera calibration images (cf.\ Section~\ref{sec:approach:geometry}) of a chessboard calibration pattern with $6~\times~4$ corners ($7~\times~5$ squares) and feeding the images as input to our camera calibration module. Separately, for each of the 15 target locations, we produced a projector calibration image (cf.\ again Section~\ref{sec:approach:geometry}) by projecting a $11~\times~4$ asymmetrical circle pattern image to the location in question using the steerable mirror, placing a chessboard pattern beside the projected pattern, and acquiring the image using the downward-facing camera. We then fed these images alongside the output of the camera calibration module to our projector calibration module. For each of the target locations, the steerable mirror was made to point to that location, the asymmetrical circle pattern image was projected to the scene plane, an image was acquired using the camera, and the location was registered in the MDC-X software as a preset. The output of the projector calibration module is a homography per input projector calibration image (cf.\ Section~\ref{sec:approach:homography}). Next, we warped the images to be projected to the respective locations using their corresponding homography, using a third dedicated custom module. These warped images were finally imported into the MDC-X software and associated with their respective location presets (cf.\ Figure \ref{fig:eval}(b)).

>>>>

\begin{abstract}
Augmented reality (AR) promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene, potentially reducing or altogether obviating the need for workers to refer to instructions in paper form or on a screen. \textit{Spatial} AR, in turn, is a form of AR whereby the augmentation of the scene is carried out using a projector, with the advantage of rendering the augmentation visible to all onlookers simultaneously without calling for each to wear some form of head-mounted display. In carrying out spatial AR, however, care must be taken to appropriately warp the images to be projected in a manner that they appear free of distortions to the viewer. For planar scene geometry (such as a floor, wall, or table), this can be done in a cumbersome manual process called keystone correction---often using software bundled with the projector---to compute an appropriate corrective image warp. %, since the geometry of the scene as it relates to the geometry of the projector plays a role in how the pixels of the projector's image plane map to points in the scene

@@

Correcting for projective distortions of the sort outlined in Section~\ref{sec:intro} can be achieved by modeling the manner in which the respective rays through the pixels of the projector's image plane fan out into the scene (i.e., by `calibrating' the projector) and the geometry of the scene itself (i.e., by recovering the scene plane relative to the projector) within at least the projector's field of view. This is because the scene point `illuminated' by a pixel in the projector's image plane can be recovered by intersecting its corresponding ray with the geometry of the scene surface. To model this interaction, we (i) carry out a one-time projector calibration, which in our approach calls for additionally calibrating a camera facing downwards to the scene plane and includes recovery of the scene plane as a convenient side effect. Next, we use the relative camera-projector-scene plane geometry to (ii) compute a plane-induced homography that warps the image to be projected in a manner that it appear undistorted to the viewer, and placed in alignment with the axes of a proxy image of the scene. These two points are treated in Sections~\ref{sec:approach:geometry} and \ref{sec:approach:homography}, respectively.

@@

\begin{figure}
    \centerline{\includegraphics[scale=.35]{images/2d3d.png}}
    \caption{Scene plane (gray) recovered via spatial resection with respect to 2D-3D correspondences obtained using a chessboard pattern (blue); 3D circle center points of the asymmetrical circle pattern---i.e., the 3D positions of the 2D-3D correspondences to be used for calibrating the projector---obtained by intersection with the scene plane of back-projections (likewise gray) of the 2D circle center points of the asymmetrical circle pattern detected in the image plane (red). Note that as in the figures of this section that follow, the rendering in the figure corresponds to the projection calibration image in Figure~\ref{fig:2d}(b), acquired by the downwards-facing camera (frustum of the camera in black, with up vector in red).}
    \label{fig:3d}
\end{figure}

@@

Owing to the manner in which we place the virtual projector, the virtual projector's axes and thus the augmentation are aligned with the axes of the downwards-facing camera; the placement of the camera thereby intuitively determines the principal axes according to which augmentations are to be placed. Note further that a consequence of placing the virtual projector by rotating about the point of intersection of the projector's optical axis with the scene plane is that \textit{the center of the projector's image plane remains invariant} to the placement of the virtual projector, i.e., a steerable mirror can be aimed with respect to a point projected from the center of the projector's image plane, further facilitating placement of augmentations.

@@

The hardware setup employed in the evaluation (cf.\ Figure \ref{fig:eval}(a)) comprised a Panasonic PT-RZ660BE projector with a steerable mirror system---used in our experiments to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute \cite{rupprecht2020information,Rupprecht2021}. The steerable mirror system was bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a downwards-facing Zed 2 stereo camera manufactured by Stereolabs, yet relied only on the left view. The floorspace used for our experiments measured dimensions of ca.\ 6~m~$\times$~4~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m.

@@

\paragraph{Our approach} We began by carrying out a calibration of the camera, acquiring 10 camera calibration images (cf.\ Section~\ref{sec:approach:geometry}) of a chessboard calibration pattern with $6~\times~4$ corners ($7~\times~5$ squares) and feeding the images as input to our camera calibration module. Separately, for each of the 15 target locations, we produced a projector calibration image (cf.\ again Section~\ref{sec:approach:geometry}) by projecting a $11~\times~4$ asymmetrical circle pattern image to the location in question using the steerable mirror, placing a chessboard pattern beside the projected pattern, and acquiring the image using the downwards-facing camera. We then fed these images alongside the output of the camera calibration module to our projector calibration module. For each of the target locations, the steerable mirror was made to point to that location, the asymmetrical circle pattern image was projected to the scene plane, an image was acquired using the camera, and the location was registered in the MDC-X software as a preset. The output of the projector calibration module is a homography per input projector calibration image (cf.\ Section~\ref{sec:approach:homography}). Next, we warped the images to be projected to the respective locations using their corresponding homography, using a third dedicated custom module. These warped images were finally imported into the MDC-X software and associated with their respective location presets (cf.\ Figure \ref{fig:eval}(b)).
